### 2013-12-16 research/paper/results/results-2.3.tex
Committing text changes and suggestions through to the end of the paper. Still need to go back and make sure our parameters are understood in terms of Parkinson's work

\subsection{Galloping response and natural frequency}

@@

The maximum mean power at different $m^*$ (Fig.\ref{fig:m_star_collapsed}(a)) was constant for $m^*>30$ in the low \reynoldsnumber\ case. However, at $m^* \leq 30$, the power output reduces with reducing $m^*$ across the parameter range. However, when the sinusoidal forcing function in Eq.\ref{equationofmotion} which cater for the vortex shedding was disregarded, the reduction in power could not be observed Fig.\ref{fig:m_star_collapsed}(b). The suppression of galloping response at low $m^*$ due to the presence of vortex shedding has previously been observed by \cite{Joly2012}. This is a non-linear interaction between the forcing that drives the galloping excitation and the forcing as a result of vortex shedding. The forcing associated with vortex  shedding is significantly larger and at a higher frequency than the forcing that drives galloping. Systems with low $m^*$ do not have enough inertia to fully sustain the galloping excitation over the longer period.

At \reynoldsnumber=22300 power output started to increase for cases with $m^*<50$. The overall mean power tend to increase  as the $m^*$ was decreased when $U^*$ was kept constant (Fig\ref{fig:mstarcollapsed_parkinson} (a)). The same effect was observed when $U^*$ was increased keeping $m^*$ constant (\ref{fig:mstarcollapsed_parkinson} (b)). It should be noted that the influence of $U^*$ was observed only for low mass ratios.  The velocity time traces of example cases of both scenarios presented in Fig.\ref{time_hostory_mstar_mass} and \ref{time_history_mstar_ustar} shows that essentially the same phenomenon occurring in both cases whereby the velocity signal tend to shift from a sinusoidal signal towards a square wave. The corresponding displacement signal tend to become more like a triangular wave. When the inertia of the system reduces, the body can accelerate faster thus attaining higher velocities more rapidly and spend a higher proportion of the period at a high velocity. Higher velocities are favourable because they result in higher instantaneous hydrodynamic forcing and power output from mechanical damping. However, the velocity is limited by the characteristic of the hydrodynamics forcing which reaches a maximum and then decreases past an incident angle of of $13.21^{\circ}$ which correspond to a transverse velocity of $\frac{\dot{y}}{U}=0.235$.It is estimated that the efficiency limit i.e ($\ustar \rightarrow \infty$, $m^* \rightarrow 0$ and $\frac{c}{\rho U \mathcal{A}}=1.22$) will approach $13.5\%$ which corresponds to a square wave velocity signal with a velocity amplitude that results in maximum  hydrodynamic forcing. Physical systems may not realize the full potential due to practical limitations. Increasing $U^*$ effectively reduces the stiffness of the system and lengthen the period, thus again allowing a larger portion of the period to be at a high velocity which favours power output. For the case of fixing $U^*$ and decreasing $m^*$ in (Fig\ref{fig:mstarcollapsed_parkinson} (a)), the lengthening of the period is associated with the added mass which is kept constant at 3.5 being more dominant on the overall mass of the system when m* is reduced.

@@

\subsection{Comparison with FSI simulations}
 Similar trends were captured for both displacement and velocity amplitudes between QSS and FSI simulations (Fig. \ref{fig:FSI_QSS_compare}(a) and \ref{fig:FSI_QSS_compare}(b)). Quantitatively a large discrepancy (average of $30\%$) could be observed between QSS and FSI data. Therefore the power also becomes significantly low in FSI data (Fig.\ref{fig:FSI_QSS_compare} (c)). However, the FSI data (Fig.\ref{fig:FSI_QSS_compare} (c)) were able to produce the main the rise and the fall of mean power when $U^*$ was increased. The reasoning behind this fact is that galloping is weak at \reynoldsnumber$=165$  and therefore fluid damping has a significant effect. It was reported by \cite{Barrero-Gil2009} that galloping only starts to occur ar Re $\geq 159$. As power is a function of $(\dot{y})^2$ the error between QSS and FSI power is compounded.

@@

In this paper, the power transfer of a square body under aero elastic galloping is analysed by solving the quasi-steady state model equations through numerical integration. At higher $m^*$ ($m^8>30$ at lower \reynoldsnumber and $m^*> 50$ at high \reynoldsnumber) the power output of the system is not dependent on \ustar or natural frequency of the system, but controlled by the non-dimensionalised damping constant $\frac{c}{\rho U \mathcal{A}}$ . By analysing key regions of the power vs \ustar curve it could be concluded that in order to obtain an optimum power output, the damping constant ($\frac{c}{\rho\mathcal{A}U}$) should be high, but not excessive until it  to hinders the galloping from reaching induced angles of attack where the forcing is significant. The effect of mass ratio was could also be observed where at \reynoldsnumber=165. The peak efficiency was found out to be $0.26\%$ for \reynoldsnumber=165 and $6.7\%$ for \reynoldsnumber=22300  when $\frac{c}{\rho \mathcal{A}U}=0.314$ and $\frac{c}{\rho \mathcal{A}U}=1.04$ respectively. The mean power tend to decrease at $m^*<50$ which was found out to be an influence of vortex shedding. At \reynoldsnumber=22300 an opposite result could be observed where the mean power tend to increase with decreasing mass ratio as well as the mean power tend to increase with increasing $U^*$ at low mass ratios. When the mass ratio decreases, due to the lower inertia the velocity time trace tend to move from a sinusoidal signal towards a square signal where it sustains high velocities for longer periods of time which leads to a higher mean power output. The limit to peak efficiency was found out to be $13.5\%$ and occurs when $m^*\rightarrow 0$ and $\ustar \rightarrow \infty$ and $\frac{c}{\rho \mathcal{A}U}=1.22$ by analysing the data trend by lowering the $m^*$

>>>>

\subsection{Galloping response and governing parameters}

@@

The mean power at different $m^*$ is presented as a function of the mass-damping parameter $\Gamma_2$ in figure \ref{fig:m_star_collapsed}(a) for the low \reynoldsnumber\ case. For $m^*>30$, the power output is essentially independent of $m^*$, while at $m^* \leq 30$, the power output reduces with reducing $m^*$ across the parameter range. However, when the sinusoidal forcing function in equation \ref{equationofmotion}, which caters for the vortex shedding, is disregarded, the reduction in power is not observed as shown in figure \ref{fig:m_star_collapsed}(b). The suppression of galloping response at low $m^*$ and low \reynoldsnumber\ due to the presence of vortex shedding has previously been observed by \cite{Joly2012}. This is a non-linear interaction between the forcing that drives the galloping excitation and the forcing as a result of vortex shedding. The forcing associated with vortex  shedding is significantly larger and at a higher frequency than the forcing that drives galloping. Systems with low $m^*$ do not have enough inertia to fully sustain the galloping excitation over the longer period.

At $\reynoldsnumber=22300$ power output started to increase for cases with $m^*<50$. The overall mean power tend to increase as the $m^*$ was decreased when $U^*$ was kept constant (Fig\ref{fig:mstarcollapsed_parkinson} (a)). The same effect was observed when $U^*$ was increased keeping $m^*$ constant (\ref{fig:mstarcollapsed_parkinson} (b)). It should be noted that the influence of $U^*$ was observed only for low mass ratios.  The velocity time traces of example cases of both scenarios presented in Fig.\ref{time_hostory_mstar_mass} and \ref{time_history_mstar_ustar} shows that essentially the same phenomenon occurring in both cases whereby the velocity signal tend to shift from a sinusoidal signal towards a square wave. The corresponding displacement signal tend to become more like a triangular wave. When the inertia of the system reduces, the body can accelerate faster thus attaining higher velocities more rapidly and spend a higher proportion of the period at a high velocity. Higher velocities are favourable because they result in higher instantaneous hydrodynamic forcing and power output from mechanical damping. However, the velocity is limited by the characteristic of the hydrodynamics forcing which reaches a maximum and then decreases past an incident angle of of $13.21^{\circ}$ which correspond to a transverse velocity of $\frac{\dot{y}}{U}=0.235$.It is estimated that the efficiency limit i.e ($\ustar \rightarrow \infty$, $m^* \rightarrow 0$ and $\frac{c}{\rho U \mathcal{A}}=1.22$) will approach $13.5\%$ which corresponds to a square wave velocity signal with a velocity amplitude that results in maximum  hydrodynamic forcing. Physical systems may not realize the full potential due to practical limitations. Increasing $U^*$ effectively reduces the stiffness of the system and lengthen the period, thus again allowing a larger portion of the period to be at a high velocity which favours power output. For the case of fixing $U^*$ and decreasing $m^*$ in (Fig\ref{fig:mstarcollapsed_parkinson} (a)), the lengthening of the period is associated with the added mass which is kept constant at 3.5 being more dominant on the overall mass of the system when m* is reduced.

\JL{KASUN, again this last paragraph is all in terms of $U^*$, but you establish earlier that $U*^$ is not the important parameter, your new damping parameter (which is actually a mass-damping parameter) is the critical parameter. Can this argument be rewritten in terms of this new parameter?}

@@

\subsection{Comparison with FSI simulations}
As the results to this point are based on solving equations which come from the quasistatic assumption, it is natural to query how these results compare to the real flow. Here, results are presented of full fluid-structure direct numerical simulations (FSI) at $\reynoldsnumber=165$ and compared to the results obtained from the quasistatic model (QSS) at the same \reynoldsnumber.

Qualitatively, the two compare very well. Similar trends were captured for both displacement and velocity amplitudes between QSS and FSI simulations as shown in figures \ref{fig:FSI_QSS_compare}(a) and \ref{fig:FSI_QSS_compare}(b). However, there is a reasonably large quantitative discrepancy (average of $30\%$) between QSS and FSI data, with the QSS model overpredicting the response of the body. Therefore the predicted power output is reduced in the FSI data, as shown in figure \ref{fig:FSI_QSS_compare}(c). However, the FSI data does produce the main rise and fall of mean power when $U^*$ was increased.

The exact reason behind this discrepancy is unclear. A possible explanation is that galloping is reasonably weak at $\reynoldsnumber=165$.  It was reported by \cite{Barrero-Gil2009} that galloping only starts to occur ar Re $\geq 159$. It may be that simulations conducted so close to the threshold for the onset of galloping are very sensitive to errors due to blockage or under-resolution, both of which can change the effective \reynoldsnumber of the flow. Small changes in effective \reynoldsnumber\ can have a significant impact of the fluid damping, and therefore on the amplitude and transverse velocity of the body. As power is a function of $(\dot{y})^2$ the error between QSS and FSI power is compounded.

@@

In this paper, the power transfer of a square body under aero elastic galloping is analysed by solving the quasi-steady state model equations through numerical integration. At higher $m^*$ ($m^*>30$ at lower \reynoldsnumber and $m^*> 50$ at high \reynoldsnumber) the power output of the system is not dependent on \ustar or natural frequency of the system, but controlled by the non-dimensionalised damping constant $\frac{c}{\rho U \mathcal{A}}$ . By analysing key regions of the power vs \ustar curve is concluded that in order to obtain an optimum power output, the mass-damping constant $\Gamma_2$ should be high, but not so excessive that it hinders the galloping from reaching induced angles of attack where the forcing is significant. The effect of mass ratio was also observed. The peak efficiency was found to be $0.26\%$ for $\reynoldsnumber=165$ and $6.7\%$ for $\reynoldsnumber=22300$  when $\Gamma_2=0.314$ and $\Gamma_2=1.04$ respectively. In the low \reynoldsnumber\ case, the mean power tends to decrease at $m^*<30$ which appears to be due to the influence of vortex shedding. At $\reynoldsnumber=22300$ the opposite is observed where the mean power tends to increase with decreasing mass ratio, as well as the mean power increasing with increasing $U^*$ at low mass ratios. For this higher \reynoldsnumber\ case, When the mass ratio decreases, due to the lower inertia the velocity time trace tend to move from a sinusoidal signal towards a square signal where it sustains high velocities for longer periods of time which leads to a higher mean power output. The limit to peak efficiency was found out to be $13.5\%$ and occurs when $m^*\rightarrow 0$ and $\ustar \rightarrow \infty$ and $\frac{c}{\rho \mathcal{A}U}=1.22$ by analysing the data trend by lowering the $m^*$.
